Uncertainty Quantification in Multiscale Models of Charge Transport in Organic Semiconductors: Influence of the Exhange-Correlation Functional

### 2025-01-03 paper.tex
typo

\subsection{Time-of-flight calculations}
And the variation in small $J_{ij}$ due to HFX has less impact on the charge dynamics. Table \ref{tab:ToF_J} shows the ToF for the MADN system after deleting the molecular connections with  $\log_{10} J_c^2 < -5$. The resulting ToF is close to the values obtained without deleting any connections (shown in Table \ref{tab:ToF_MADN_HFX}).
The increase of ToF after deleting the connections with  $\log_{10} J_c^2 < -5$ is always less than 30\%, confirming that the molecular connections with the small $J_{ij}$ has small effect in ToF.

In this section we answer the question of how does HF level change the electronic structures ($\lambda, E_i, J_{ij}$) and 
how does HF level change the ToF. 
In the next section, uncertainty quantification via Monte Carlo method and sensitivity analysis is performed to answer which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the ToF distribution. 
And further we estimate the range of the quantity of interest, given a confidence level.

The ToF is also calculated without energy disorder, meaning $\Delta E_{ij}=0$ for all $i,j$.
Table~\ref{tab:ToF_MADN_HFX} shows the ToF and corresponding diffusive velocity $v_\text{ToF}$.
With energy disorder, the ToF increases by a factor of approximately 15 as $\alpha$ increases from 0 to 0.25.  
While without energy disorder, the increase factor is about 4. This increase in ToF is attributed to the rise in $\lambda$, changes in molecular energies, and variations in coupling elements.

\begin{table}[tbp]
\caption{The ToF and diffusive velocity calculated by ToF along a distance $L_x = \unit[9.0]{nm}$ with and without energy disorder of the MADN system as a function of the HFX. The ToF is in unit $\unit[]{s}$ and $v_\text{ToF}$ in unit $\unit[]{m/s}$.}
\begin{ruledtabular}
  \begin{tabular}{c c c c }
        \ahfx & full & $J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > 5)$ & $\Delta E_{ij} =0$ \\% & $v_\text{ToF}$(no $E$) \\
    \hline
        0.00 &  $6.4 \cdot 10^{-9}$ & $7.5 \cdot 10^{-9}$ & $1.9 \cdot 10^{-10}$ \\%& 42 \\
        0.05 & $ 7.9 \cdot 10^{-9}$ & $8.1 \cdot 10^{-9}$ & $4.1 \cdot 10^{-10}$ \\%& 20 \\
        0.10 & $ 1.6 \cdot 10^{-8}$ & $1.6 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\%& 20 \\
        0.15 & $ 3.0 \cdot 10^{-8}$ & $3.1 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\%& 25 \\
        0.20 & $ 2.1 \cdot 10^{-8}$ & $2.5 \cdot 10^{-8}$ & $4.5 \cdot 10^{-10}$ \\%& 18 \\
        0.25 & $ 9.5 \cdot 10^{-8}$ & $9.7 \cdot 10^{-8}$ & $7.2 \cdot 10^{-10}$ \\%& 11 \\
    \end{tabular}
\end{ruledtabular}
\label{tab:ToF_MADN_HFX}
\end{table}

>>>>

\subsection{Time-of-flight calculations}

\begin{table}[tbp]
\caption{\bjoern{TODO:}{rewrite}The ToF and diffusive velocity calculated by ToF along a distance $L_x = \unit[9.0]{nm}$ with and without energy disorder of the MADN system as a function of the HFX. The ToF is in unit $\unit[]{s}$ and $v_\text{ToF}$ in unit $\unit[]{m/s}$.}
\begin{ruledtabular}
  \begin{tabular}{c c c c }
        \ahfx & full & $J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > -5)$ & $\Delta E_{ij} =0$ \\% & $v_\text{ToF}$(no $E$) \\
    \hline
        0.00 &  $6.4 \cdot 10^{-9}$ & $7.5 \cdot 10^{-9}$ & $1.9 \cdot 10^{-10}$ \\%& 42 \\
        0.05 & $ 7.9 \cdot 10^{-9}$ & $8.1 \cdot 10^{-9}$ & $4.1 \cdot 10^{-10}$ \\%& 20 \\
        0.10 & $ 1.6 \cdot 10^{-8}$ & $1.6 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\%& 20 \\
        0.15 & $ 3.0 \cdot 10^{-8}$ & $3.1 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\%& 25 \\
        0.20 & $ 2.1 \cdot 10^{-8}$ & $2.5 \cdot 10^{-8}$ & $4.5 \cdot 10^{-10}$ \\%& 18 \\
        0.25 & $ 9.5 \cdot 10^{-8}$ & $9.7 \cdot 10^{-8}$ & $7.2 \cdot 10^{-10}$ \\%& 11 \\
    \end{tabular}
\end{ruledtabular}
\label{tab:ToF_MADN_HFX}
\end{table}

From the analysis of reorganization energies, site energies, and electronic coupling elements for different values of \ahfx, it is not clear how the mostly on distribution-level observed variations impact the overall charge transport properties. To scrutinize the dependence of such a material property, we now calculate the time-of-flight $\tau$ and report the respective values in Table~\ref{tab:ToF_MADN_HFX}. Here, we refer with ''full'' to time-of-flight obtained for the the as-calculated charge transport network. One can see that $\tau$ varies by roughly one order of magnitude between $\ahfx=0$ ($\unit[6.3\cdot 10^{-9}]{s}$) and $\ahfx=0.25$ ($\unit[9.5\cdot 10^{-8}]{s}$), with an almost monotonous increase. When the squared coupling elements with values below $\unit[10^{-5}]{(eV)^2}$ are set to zero ($J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > -5)$), one obtains only minimally, but consistently, larger $\tau$, corroborating the notion that the very small coupling elements are of little relevance for charge transport. Finally, we also consider the case in which the energetic disorder is ignored ($\Delta E_{ij}=0$). Here, one also can see (next to the generally shorter time-of-flight) a consistent increase in $\tau$, however only by a factor of about \unit[3.8]{}, a combined effect of the increased reorganization energy and variations in coupling elements.
